Paper_analyses

### 2021-11-15 Paper_Analyses_subj_obje_arousal.Rmd
initialise PCA with inference

all.data$TAS_mediansplit<- if_else(all.data$TAS> median(all.data$TAS), "High", "Low")
all.data$AQ_mediansplit<- if_else(all.data$AQ> median(all.data$AQ), "High", "Low")
 # design
var.design_asd <- as.factor(all.data$Group)
var.design_aq <- as.factor(all.data$AQ_mediansplit)
var.design_tas <- as.factor(all.data$TAS_mediansplit)
colnames(all.data)

var.data <- all.data[,c(6:172)]

var.PCA.inf_asd <-InPosition::epPCA.inference.battery(var.data, 
                                       scale = FALSE, 
                                       center = FALSE, 
                                       DESIGN = var.design_asd, 
                                       make_design_nominal = TRUE, 
                                       graphs = TRUE, k = 0, 
                                       test.iters = 1000, 
                                       constrained = FALSE, 
                                       critical.value = 2)

>>>>

View(all.data1)

# exclude peope with more han 50% missign data

all.data1$per_ssid_pupil_loss_perc

all.data2<- subset(all.data1,
                   per_ssid_pupil_loss_perc< 24)

# now mean wise inputation based on each variable
all.data2

colnames(all.data2)
# pupil row-wise inputation
k <- which(is.na(all.data2[, c(1,4:59)]), arr.ind=TRUE)
k
all.data3<- all.data2
all.data3pup<- all.data2[, c(1,4:59)]

all.data3pup[k] <- rowMeans(all.data3pup[, 2:57], na.rm=TRUE)[k[,1]]

# HR
all.data3_hr<- all.data3[,c(1,60:115)]
k <- which(is.na(all.data3_hr[, 1:57]), arr.ind=TRUE)
k

all.data3_hr[k] <- rowMeans(all.data3_hr[, 2:57], na.rm=TRUE)[k[,1]]

# SCR
colnames(all.data3)
all.data3_scr<- all.data3[,c(1,116:171)]
k_scr <- which(is.na(all.data3_scr[, 1:57]), arr.ind=TRUE)
k_scr

all.data3_scr[k_scr] <- rowMeans(all.data3_scr[, 2:57], na.rm=TRUE)[k_scr[,1]]

# merge()
all.data3_forPCA<- all.data3[,1:3]

all.data3_forPCA<- left_join(all.data3_forPCA, all.data3pup)
all.data3_forPCA<- left_join(all.data3_forPCA, all.data3_hr)
all.data3_forPCA<- left_join(all.data3_forPCA, all.data3_scr)

 # design
# var.design_asd <- as.factor(all.data$Group)

colnames(all.data3_forPCA)

var.data <- all.data3_forPCA[,c(4:171)]

library(TInPosition)
library(prettyGraphs)

# inferential PCA
var.PCA.scr_hr_pup <-InPosition::epPCA.inference.battery(var.data, 
                                       scale = TRUE, 
                                       center = TRUE, 
                                       # DESIGN = var.design_asd, 
                                       # make_design_nominal = TRUE, 
                                       graphs = TRUE, k = 0, 
                                       test.iters = 1000, 
                                       constrained = FALSE, 
                                       critical.value = 2)

# includValenceMean_median_split
colnames(all.data3)

all.data3_val<- all.data3[,c(1,228:283)]

all.data3_val
k_val <- which(is.na(all.data3_val[, c(1:57)]), arr.ind=TRUE)
k_val
all.data3_val[k_val] <- rowMeans(all.data3_val[, 2:57], na.rm=TRUE)[k_val[,1]]

all.data3_forPCA_withval<- left_join(all.data3_forPCA, all.data3_val)

# subjective arousal

all.data3_ar<- all.data3[,c(1,172:227)]

all.data3_ar
k_ar <- which(is.na(all.data3_ar[, c(1:57)]), arr.ind=TRUE)
k_ar
all.data3_ar[k_ar] <- rowMeans(all.data3_ar[, 2:57], na.rm=TRUE)[k_ar[,1]]

all.data3_forPCA_withar<- left_join(all.data3_forPCA, all.data3_ar)

library(InPosition)
var.PCA.scr_hr_pup_val <-InPosition::epPCA.inference.battery(all.data3_forPCA_withval[,4:226], 
                                       scale = TRUE, 
                                       center = TRUE, 
                                       # DESIGN = var.design_asd, 
                                       # make_design_nominal = TRUE, 
                                       graphs = TRUE, k = 0, 
                                       test.iters = 1000, 
                                       constrained = FALSE, 
                                       critical.value = 2)

# with self arousal
var.PCA.scr_hr_pup_ar <-InPosition::epPCA.inference.battery(all.data3_forPCA_withar[,4:227], 
                                       scale = TRUE, 
                                       center = TRUE, 
                                       # DESIGN = var.design_asd, 
                                       # make_design_nominal = TRUE, 
                                       graphs = TRUE, k = 0, 
                                       test.iters = 1000, 
                                       constrained = FALSE, 
                                       critical.value = 2)
